Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-17 ms.tex
updated sections on Asic dewar

@@

\clearpage
\subsection{Asic Dewar Tests}

@@

\subsubsection{Pre-Ampflier Reset Test}
We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
We used a stripe mode 2048x256 with reference pixels on the bottom and sides.
\begin{figure*}
{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.99\textwidth}{No Reference Pixels RPF}}}
{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.99\textwidth}{Reference Pixel RPF}}}
\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
\end{figure*}

\subsubsection{Stripe versus Window Mode}
\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode TIme Series}
\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:stripeVsWindowAZlab04}
\end{figure*}

>>>>

\author{Kenneth Don}
\affiliation{Steward Observatory \\
933 North Cherry Avenue \\
Tucson, AZ 85721, USA}

@@

\clearpage
\subsection{Asic Dewar Tests}
We performed a variety of stability tests using a dewar with the same type of detectors, readout electronics and temperature control as the in-flight parts.
The detectors and asic controllers are devices that did not fully meet the flight requirements for NIRCam, but in many cases are close or above requirements.
The detectors are illuminated by short wavelength LEDs (1.6 to 1.8~$\mu$m) or long wavelength (\textbf{Which type and wavelength?}) LEDs.
The LEDS are type Lms17 and ???? from Electro Optical Components, Inc.

The dewar has limited space for optical illumination so the LEDS light is bounced off a convex mirror and painted aluminum surface before reaching the detectors.
The convex mirror, its support structure and a black mask at the edges of the detectors all produce a shadows on some pixels of the detector.
The illuminated portions of the detector are used for aperture extractions while the shadows are used for background subtraction apertures.

No LEDs used in ground-based tests were as stable as the desired precisions relevant to exoplanet targets (sub 30 ppm), so multiple arrays are used to correct for lamp variations during illuminated stability tests.
The best absolute stability of an LED measured on a detector was 0.05\% ppm over 2 hours.
More typically, the variations were 1\%, although the current measured with a multimeter was stable to 0.1\%.
A ratio time series is constructed by dividing the time series derived from one detector to another time series from a different detector.

@@

\subsubsection{Pre-Ampflier Reset Test}
We also explored the difference between resets per frame versus resets per integrations as discussed in Section \ref{sec:preAmp}.
We used a stripe mode 2048x256 with reference pixels on the bottom and sides.

Each pre-amplifier is reset once per frame by the current flight parameters.
This causes amplifier offsets because each amplifier is reset to a different value with some noise, as visible in Figure \ref{fig:RPFrefpix}.
The pre-amplifier resets, however, can be largely corrected for by reference pixels or background subtraction.
Figure \ref{fig:RPFrefpix} also shows a corrected image where the top reference pixels (a 512 pixel wide 4 pixel tall region per amplifier) is used to subtract the amplifier offsets.

\begin{figure*}
{\gridline{\fig{rpf_vs_rpi_old_cds_no_refpix.pdf}{0.99\textwidth}{No Reference Pixels RPF}}}
{\gridline{\fig{rpf_vs_rpi_new_cds_with_refpix.pdf}{0.99\textwidth}{Reference Pixel RPF}}}
\caption{Reset per frame with reference pixel correction.}\label{fig:RPFrefpix}
\end{figure*}

\subsubsection{Stripe versus Window Mode}
JWST users may select between two types of subarrays within NIRCam grism time series.
This is specified with the Astronomy Proposal Tools (APT) software in the ``NIRCam Grism Time Series'' template with "No. of Output Channels".
When the output channels are set to 4 (stripe mode), the frame time is approximately four times faster than 1 output channel (window mode).
The exact timing is slightly different than a factor of 4 due to overheads.
The advantage of stripe mode is that it allows more samples up the ramp in an integration and also shorter minimum integration times to enable observations of brighter sources.
The stripe mode uses four different amplifiers, which could potentially lead to differences between the 4 regions each 512 pixels wide.
The stripe mode is the same as standard full frame imaging when the height of the stripe is 2048 pixels tall.

Figure \ref{fig:stripeVsWindowAZlab04} shows the time series for a stripe versus window mode test.
In each case, these are the ratios of time series between two Long wavelength detectors derived from aperture photometry with background subtraction.

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.49\textwidth}{Stripe Mode TIme Series}
\fig{azlab_ratio_tser_window.pdf}{0.49\textwidth}{Window Mode Time series}}}
\caption{Stripe mode (4 output amplifiers) gives better precision than window mode (one amplifier).}\label{fig:stripeVsWindowAZlab04}
\end{figure*}
